05_DESeq_manipulation

### 2019-05-16 analysis/05_DESeq2_manipulate.Rmd
2 heatmaps for all
update levels

# set levels
m.colData$treatment <- factor(m.colData$treatment, levels = 
                              c("m.inc.d3",  "m.inc.d9",
                                "m.inc.d17", "m.n2",
                                "m.inc.d8", "prolong", "extend"))

@@

m.colData$outcome <- ifelse(grepl("d3|d9|d17|n2", m.colData$treatment), "remove", 
                     ifelse(grepl("d8", m.colData$treatment),"early",
                     ifelse(grepl("prolong", m.colData$treatment),"prolong",
                     ifelse(grepl("extend", m.colData$treatment),"extend", NA))))
m.colData$outcome <- factor(m.colData$outcome, levels = 
                              c("remove",  "prolong",
                                "early", "extend"))
summary(m.colData[c(7,3,4,5,8,9)])
```

@@

```{r althings, eval = T}

## subset for test

m.colData <- m.colData %>%
  filter(sextissue == "female_pituitary") %>%
  droplevels()

@@

dat$V1 <- factor(dat$V1, levels = 
                              c("m.inc.d3",  "m.inc.d9",
                                "m.inc.d17", "m.n2",
                                "m.inc.d8", "prolong", "extend"))
dat$V2 <- factor(dat$V2, levels = 
                              c("m.inc.d3",  "m.inc.d9",
                                "m.inc.d17", "m.n2",
                                "m.inc.d8", "prolong", "extend"))

@@

dat$V1 <- factor(dat$V1, levels = 
                              c("remove",  "prolong",
                                "early", "extend"))
dat$V2 <- factor(dat$V2, levels = 
                              c("remove",  "prolong",
                                "early", "extend"))

>>>>

# set levels
m.colData$treatment <- factor(m.colData$treatment, levels = 
                              c("m.inc.d3",  "m.inc.d8",
                                "m.inc.d9", "m.inc.d17",
                                "prolong", "extend", "m.n2"))

@@

m.colData$outcome <- ifelse(grepl("d3|d9|d17", m.colData$treatment), "end inc", 
                     ifelse(grepl("d8|n2", m.colData$treatment),"end hatch",
                     ifelse(grepl("prolong", m.colData$treatment),"prolong inc",
                     ifelse(grepl("extend", m.colData$treatment),"delay hatch", NA))))

m.colData$outcome <- factor(m.colData$outcome, levels = 
                              c("end inc",  "end hatch",
                                "prolong inc", "delay hatch"))
summary(m.colData[c(7,3,4,5,8,9)])
```

@@

```{r althings, eval = T}
## subset for test 
#m.colData <- m.colData %>%
#  filter(sextissue == "female_pituitary") %>%
#  droplevels()

@@

dat$V1 <- factor(dat$V1, levels = 
                              c("m.inc.d3",  "m.inc.d8",
                                "m.inc.d9", "m.inc.d17",
                                "prolong", "extend", "m.n2"))
dat$V2 <- factor(dat$V2, levels = 
                              c("m.inc.d3",  "m.inc.d8",
                                "m.inc.d9", "m.inc.d17",
                                "prolong", "extend", "m.n2"))

@@

dat$V1 <- factor(dat$V1, levels = 
                              c("end inc",  "end hatch",
                                "prolong inc", "delay hatch"))
dat$V2 <- factor(dat$V2, levels = 
                              c("end inc",  "end hatch",
                                "prolong inc", "delay hatch"))
